Response to reviewers

### 2024-11-30 Manuscript/ecography_reponse_letter.tex
Update ecography_reponse_letter.tex

\textcolor{blue}{Line 194-195. Please improve clarity.}

%  @@@TODO: rewrite following other reviewers comments (stats for results)

\textcolor{blue}{Line 201-203. Please simplify and improve clarity.}

%  @@@TODO: rewrite following other reviewers comments (stats for results)

\textcolor{blue}{Line 207-211. Please provide a clearer explanation of the effect size and statistical significance of these model outcomes, similar to the explanation provided in lines 198-201.}

%  @@@TODO: rewrite following other reviewers comments (stats for results)
%  @@@TODO: calculate effect sizes
We now added all the statistics results in the supplementary results from table 6 to 18.

@@

%  @@@TODO: name of the two added marine species

@@

%  @@@TODO: Rerun the simulations with 400, 800 and 1000 elements.
%  But also highlight that 40 species is already quite big
% We can also link that to the use of FD in palaeontology (disparity) where 40 is also already quite big!
% Tom's comment: *Reviewer 2's point about why we use only 200 data points - it's a while since I read our paper, but I guess we did that to make it more realistic in terms of the sample sizes people use. In island studies, 200 is pretty large, and I have many references (including my own ...) where people calculate FD using 1-5 species. So again we could make the argument that it represents a trade-off, between realistic sample sizes that people analyse vs large enough that we can really test the mechanisms

@@

\textcolor{blue}{LL 170-178: why then did the authors not simply generate more data points (see my comment above)?}
%  @@@TODO: Rerun the simulations with 400, 800 and 1000 elements.

>>>>

\textcolor{blue}{Line 194-195. Please improve clarity.}
\textcolor{blue}{Line 201-203. Please simplify and improve clarity.}
\textcolor{blue}{Line 207-211. Please provide a clearer explanation of the effect size and statistical significance of these model outcomes, similar to the explanation provided in lines 198-201.}

We rewrote this entire section to hopefully improve clarity:

\textit{To understand the ability of each metric to capture a mechanism of interest, we compared their scores relative to the same metric scores of a null mechanism.
To ease interpretation of the results across a range of metrics with different orders of magnitudes of outputs and different random simulations, we first calculated the difference between the stressor of interest and the null stressor (e.g. $metric_{stressor20\%} - metric_{null20\%}$).
We then scaled these differences to be relative to the highest relative differences between all the simulations for that one metric and stressor (across the 4 levels of removal - 20\%, 40\%, etc.)
This resulted in each metric being scaled between $-1$ and $1$ where a negative difference can be interpreted as the random removal of elements leading to a higher metric score; a positive difference as the focal removal of elements (i.e. approximating equalisation, facilitation, filtering and competition) leading to a higher metric score; and a difference near $0$ meaning both the null stressor and the focal stressor having a similar effect on the metric score (Figs 1, 2 and 3).
We interpret this last scenario as the metric score being unable to clearly distinguish between a random removal of elements and a non random one.
To assess these poor performances, we compared the distributions of the $171$ scores for each metric with each reduction level for each non-null stressor to the null stressor using pairwise t-tests.
The results of these tests are displayed in figure 2 (for the non-null stressor, grey distributions are not clearly distinguishable from the null stressor).}
Lines 273-290.

Furtheremore, we have also added all the statistics results in the supplementary results from table 6 to 18 (including effect sizes).

@@

We now changed the sentence to:
\textit{We also added two marine species to the prehistoric species list (}Haliaeetus albicilla\textit{ and }Pterodroma hypoleuca\textit{);}. Lines 309-310.

@@

We re-ran the simulations with 500 and 1000 observations for 2D and 4D traits (now in the supplementary figures 3 and 4).
We did not however changed the main results in the manuscript because we believe that datasets with a low number of observations are actually not that uncommon across evolutionary biology (e.g. in palaeontology) and ecology.
For example, in island studies, 200 observations is a pretty large number (e.g. the empirical dataset in this paper).
We believe that 200 to 40 observations remains a fair trade-off between realistic sample sizes that researchers often analyse (e.g. Matthews et al. 2023) \textit{versus} much larger ones that are sometimes used (e.g. Guillerme et al. 2023).

@@

\textcolor{blue}{LL 170-178: why then did the authors not simply generate more data points (see my comment above)?}

We have now added the results for 500 and 1000 observations in the supplementary figures 4 and 5.
